The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging with the Owens Valley Long Wavelength Array

### 2017-05-06 paper.tex
touchups

The process of Tikhonov regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for
some arbitrary value of $\epsilon > 0$ chosen by the observer. The solution that minimizes this
expression is given by
\begin{equation}\label{eq:tikhonov-solution}
    \atikh = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
\end{equation}
Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
matrix's singularity. We can see this by using the singular value decomposition (SVD) of the matrix
$\b B = \b U \b \Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
\[
    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,.
\]
The diagonal elements of $\b\Sigma$ are the singular values of $\b B$ and so the contribution of
each singular component to the Tikhonov-regularized solution is scaled by $\sigma / (\sigma^2 +
\epsilon)$, where $\sigma$ is the singular value for the given singular component. Tikhonov
regularization therefore acts to suppress any component for which $\sigma\lesssim\sqrt{\epsilon}$.
If $\sigma = 0$, the component is set to zero.

In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
purposes we now assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
Tikhonov-regularized spherical harmonic coefficients $\b C = \left\langle\atikh^*\atikh\right\rangle
- \left\langle\atikh\right\rangle\left\langle\atikh^*\right\rangle$ is
\begin{equation}
    \b C = n \b V \b\Sigma^2 (\b\Sigma^2 + \epsilon\b I)^{-2} \b V^*\,.
\end{equation}
Each singular component is scaled by a factor of $\sigma^2/(\sigma^2 + \epsilon)^2$.
In the absence of Tikhonov regularization ($\epsilon=0$)
singular components with the smallest singular values -- the ones that the interferometer is
the least sensitive to -- actually come to dominate the covariance of the measured spherical
harmonic coefficients. Tikhonov regularization improves this situation by downweighting these
components.

@@

In practice, the L-curve should be used as a guide to estimate a reasonable value of $\epsilon$.
However better results can often be obtained by tuning the value of $\epsilon$. For instance
increasing the value of $\epsilon$ can improve the noise properties of the map by down-weighting
noisy modes. Decreasing the value of $\epsilon$ can improve the resolution in the map by
up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
imaging where robust weighting schemes can be tuned to similar effect.

@@

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{ccc}
        \# & $\nu$ / MHz & $\Delta\nu$ / MHz \\ \hline
        1 & 36.528 & 0.024 \\
        2 & 41.760 & 0.024 \\
        3 & 46.992 & 0.024 \\
        4 & 52.224 & 0.024 \\
        5 & 57.456 & 0.024 \\
        6 & 62.688 & 0.024 \\
        7 & 67.920 & 0.024 \\
        8 & 73.152 & 0.024 \\
    \end{tabular}
    \caption{Summary of the produced maps}
\end{table}

@@

\todo{Cite Abhilash, Eastwood 2016}

@@

>>>>

The process of Tikhonov regularization minimizes $\|\b v - \b B\b a\|^2 + \epsilon\|\b a\|^2$ for
some arbitrary value of $\epsilon > 0$ chosen by the observer. The solution that minimizes this
expression is given by
\begin{equation}\label{eq:tikhonov-solution}
    \atikh = (\b B^*\b B + \epsilon\b I)^{-1}\b B^*\b v\,.
\end{equation}
Tikhonov regularization adds a small value $\epsilon$ to the diagonal of $\b B^*\b B$, fixing the
matrix's singularity. We can see this by using the singular value decomposition (SVD) of the matrix
$\b B = \b U \b \Sigma \b V^*$. Equation~\ref{eq:tikhonov-solution} becomes
\begin{equation}
    \atikh = \b V (\b\Sigma^2 + \epsilon \b I)^{-1}\b\Sigma \b U^*\b v\,,
\end{equation}
where
\[
    \b\Sigma = \left(
        \begin{array}{ccc}
            \sigma_1 & & \\
                     & \sigma_2 & \\
                     & & \ddots \\
        \end{array}
    \right)\,.
\]
The diagonal elements of $\b\Sigma$ are the singular values of $\b B$ and so the contribution of
each singular component to the Tikhonov-regularized solution is scaled by $\sigma_i / (\sigma_i^2 +
\epsilon)$, where $\sigma_i$ is the singular value for the $i$th singular component. Tikhonov
regularization therefore acts to suppress any component for which $\sigma_i\lesssim\sqrt{\epsilon}$.
If $\sigma_i = 0$, the component is set to zero.

In practice the measurement $\b v$ is corrupted by noise with covariance $\b N$. For illustrative
purposes we will assume that $\b N=n\b I$ for some scalar $n$. In this case the covariance of the
Tikhonov-regularized spherical harmonic coefficients is
\begin{equation}
    \b C = n \b V (\b\Sigma^2 + \epsilon\b I)^{-2} \b\Sigma^2 \b V^*\,.
\end{equation}
Each singular component is scaled by a factor of $\sigma_i^2/(\sigma_i^2 + \epsilon)^2$.
In the absence of Tikhonov regularization ($\epsilon=0$)
singular components with the smallest singular values -- the ones that the interferometer is
the least sensitive to -- actually come to dominate the covariance of the measured spherical
harmonic coefficients. Tikhonov regularization improves this situation by downweighting these
components.

@@

In practice, the L-curve should be used as a guide to estimate a reasonable value of $\epsilon$.
However better results can often be obtained by tuning the value of $\epsilon$. For instance
increasing the value of $\epsilon$ can improve the noise properties of the map by down-weighting
noisy modes. Decreasing the value of $\epsilon$ can improve the resolution in the map by
up-weighting the contribution of longer baselines, which are likely fewer in number. In this respect
choosing the value of $\epsilon$ is analagous to picking the weighting scheme in traditional
imaging where robust weighting schemes can be tuned to similar effect. \todo{citation}

@@

\begin{itemize}
    \item declination dependent flux scale errors
    \item failure to reconcile observations from two separate times
\end{itemize}

@@

\begin{table*}[t]
    \centering
    \begin{tabular}{ccccc}
        \hline\hline
        \# & $\nu$ / MHz & $\Delta\nu$ / MHz
           & $\theta$ / arcmin  & noise / Jy \\ \hline
        1 & 36.528 & 0.024 & & \\
        2 & 41.760 & 0.024 & & \\
        3 & 46.992 & 0.024 & & \\
        4 & 52.224 & 0.024 & & \\
        5 & 57.456 & 0.024 & & \\
        6 & 62.688 & 0.024 & & \\
        7 & 67.920 & 0.024 & & \\
        8 & 73.152 & 0.024 & & \\
        \hline\hline
    \end{tabular}
    \caption{Summary of the produced maps}
\end{table*}

@@

\todo{Cite Abhilash, Eastwood 2017}

@@

These maps are pretty cool.
